Statistical Inference for inter-arrival times of extreme events in bursty time series

### 2020-07-26 article_springer/article_springer.Rmd
make grey lines transparent to improve plot

bibliography: CTRMstats.bib
csl: elsevier-harvard.csl
output: 
  rticles::elsevier_article:
    number_sections: true
    fig_caption: yes

@@

mean_n200<-hill_plot_values %>% group_by(x) %>% summarize(mean=mean(y))
p1<-hill_plot_values %>% ggplot() + geom_line(aes(x=x,y=y,group=rep),colour="lightgrey") +
  coord_cartesian(ylim = c(0.5, 1.5)) +
  geom_line(aes(x=x, y=mean),colour="black",data=mean_n200) + 
  ylab("Estimated tail") +
  geom_hline(yintercept=0.8, linetype="dashed", color = "red")+
  xlab("Order Statistics")+
  ylab("Hill-Estimator of Tail Index")

@@

p2<-hill_plot_values %>% ggplot() + geom_line(aes(x=x,y=y,group=rep),colour="lightgrey") +
  coord_cartesian(ylim = c(0.5, 1.5)) +
  geom_line(aes(x=x, y=mean),colour="black",data=mean_n1000) + 
  ylab("Estimated tail") +
  geom_hline(yintercept=0.8, linetype="dashed", color = "red")+
  xlab("Order Statistics")+
  ylab("Hill-Estimator of Tail Index")

@@

#logMoment estimator
logMom_Ex1_tail <-
  ggplot() + geom_line(aes(x = k, y = value, group = rep),
                       colour = "lightgrey",
                       data = tbl_estimates_tail08_logMoms_Ex1) +
  coord_cartesian(ylim = c(0.5, 1.5)) +
  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_logMoms_Ex1) + 
  ylab("Estimated tail") + geom_hline(yintercept=0.8, linetype="dashed", color = "red")

#ml estimator
mle_Ex1_tail <-
  ggplot() + geom_line(aes(x = k, y = value, group = rep),
                       colour = "lightgrey",
                       data = tbl_estimates_tail08_mles_Ex1) +
  coord_cartesian(ylim = c(0.5, 1.5)) +
  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_mles_Ex1) + 
  ylab("Estimated tail") + 
  geom_hline(yintercept=0.8, linetype="dashed", color = "red")

#Hill estimator
# hill_Ex1_tail <-
#   ggplot() + geom_line(data = tbl_estimates_tail08_hill_Ex1,
#                        aes(x = k, y = value, group = rep),
#                        colour = "lightgrey") +
#   coord_cartesian(ylim = c(0.5, 1.5)) +
#   geom_line(data=means.tbl_hill_Ex1,aes(x=k, y=mw),colour="black") + 
#   ylab("Estimated tail") +
#   geom_hline(yintercept=0.8, linetype="dashed", color = "red")+ xlab("r")

@@

#logMoment estimator
logMom_Ex2_tail <-
  ggplot() + geom_line(aes(x = k, y = value, group = rep),
                       colour = "lightgrey",
                       data = tbl_estimates_Ex2_Pareto_tail08_logMoms) +
  coord_cartesian(ylim = c(0.5, 1.5)) +
  geom_line(aes(x = k, y = mw), colour = "black", data = means.tbl_logMoms_Ex2) + 
  ylab("Estimated tail") + 
  geom_hline(yintercept=0.8, linetype="dashed", color = "red")

#ml estimator
mle_Ex2_tail <-
  ggplot() + geom_line(aes(x = k, y = value, group = rep),
                       colour = "lightgrey",
                       data = tbl_estimates_Ex2_Pareto_tail08_mles) +
  coord_cartesian(ylim = c(0.5, 1.5)) +
  geom_line(aes(x = k, y = mw), colour = "black", data = means.tbl_mles_Ex2) + 
  ylab("Estimated tail") + 
  geom_hline(yintercept=0.8, linetype="dashed", color = "red")

# #Hill estimator
# hill_Ex2_tail <-
#   ggplot() + geom_line(aes(x = k, y = value, group = rep),
#                        colour = "lightgrey",
#                        data = tbl_estimates_Ex2_Pareto_tail08_hill_times) +
#   coord_cartesian(ylim = c(0.5, 1.5)) +
#   geom_line(aes(x = k, y = mw), colour = "black", data = means.tbl_hill_times_Ex2) + 
#   ylab("Estimated tail") +
#   geom_hline(yintercept=0.8, linetype="dashed", color = "red")+ xlab("r")

@@

#logMoment estimator
logMom_Ex3_tail <-
  ggplot() + geom_line(aes(x = k, y = value, group = rep),
                       colour = "lightgrey",
                       data = tbl_estimates_Example3_Exp_logMoms) +
  coord_cartesian(ylim = c(0.5, 1.5)) +
  geom_line(aes(x = k, y = mw), colour = "black", data = means.tbl_logMoms_Ex3) + 
  ylab("Estimated tail") + 
  geom_hline(yintercept=1, linetype="dashed", color = "red")

#ml estimator
mle_Ex3_tail <-
  ggplot() + geom_line(aes(x = k, y = value, group = rep),
                       colour = "lightgrey",
                       data = tbl_estimates_Example3_Exp_mles) +
  coord_cartesian(ylim = c(0.5, 1.5)) +
  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_mles_Ex3) + 
  ylab("Estimated tail") + 
  geom_hline(yintercept=1, linetype="dashed", color = "red")

# #Hill estimator
# hill_Ex3_tail <-
#   ggplot() + geom_line(aes(x = k, y = value, group = rep),
#                        colour = "lightgrey",
#                        data = tbl_estimates_Example3_Exp_hill_times) +
#   coord_cartesian(ylim = c(0.5, 10)) +
#   geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_hill_times_Ex3) + 
#   ylab("Estimated tail") + 
#   geom_hline(yintercept=1, linetype="dashed", color = "red")+ xlab("r")
# 
grid.arrange(
  arrangeGrob(logMom_Ex1_tail,logMom_Ex2_tail,logMom_Ex3_tail,top="log-Moment"),
  arrangeGrob(mle_Ex1_tail, mle_Ex2_tail, mle_Ex3_tail,top="MLE"),
  # arrangeGrob(hill_Ex1_tail,hill_Ex2_tail,hill_Ex3_tail,top="Hill"),
  ncol=2, top="Stability plots: tail parameter"
)
```

@@

#Example One
logMom_Ex1_scale <-
  ggplot() + geom_line(aes(x = k, y = value, group = rep),
                       colour = "lightgrey",
                       data = tbl_scales_logMoms_Ex1) +
  coord_cartesian(ylim = c(0, 2)) +
  geom_line(aes(x = k, y = mw), colour = "black", means.tbl_scales_logMoms_Ex1) + 
  ylab("Estimated scale") +
  geom_hline(yintercept=1, linetype="dashed", color = "red")

mle_Ex1_scale <-
  ggplot() + geom_line(aes(x = k, y = value, group = rep),
                       colour = "lightgrey",
                       data = tbl_scales_mles_Ex1) +
  coord_cartesian(ylim = c(0, 2)) +
  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_scales_mles_Ex1) + 
  ylab("Estimated scale") +
  geom_hline(yintercept=1, linetype="dashed", color = "red")

@@

logMom_Ex2_scale <-
  ggplot() + geom_line(aes(x = k, y = value, group = rep),
                       colour = "lightgrey",
                       data = tbl_scales_logMoms_Ex2) +
  coord_cartesian(ylim = c(0, 2)) +
  geom_line(aes(x=k, y=mw),colour="black",means.tbl_scales_logMoms_Ex2) + 
  ylab("Estimated scale") + 
  geom_hline(yintercept=1, linetype="dashed", color = "red")

mle_Ex2_scale <-
  ggplot() + geom_line(aes(x = k, y = value, group = rep),
                       colour = "lightgrey",
                       data = tbl_scales_mles_Ex2) +
  coord_cartesian(ylim = c(0, 2)) +
  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_scales_mles_Ex2) + 
  ylab("Estimated scale") + 
  geom_hline(yintercept=1, linetype="dashed", color = "red")

@@

logMom_Ex3_scale <-
  ggplot() + geom_line(aes(x = k, y = value, group = rep),
                       colour = "lightgrey",
                       data = tbl_scales_logMoms_Ex3) +
  coord_cartesian(ylim = c(0, 2)) +
  geom_line(aes(x=k, y=mw),colour="black",means.tbl_scales_logMoms_Ex3) + 
  ylab("Estimated scale") + 
  geom_hline(yintercept=1, linetype="dashed", color = "red")

mle_Ex3_scale <-
  ggplot() + geom_line(aes(x = k, y = value, group = rep),
                       colour = "lightgrey",
                       data = tbl_scales_mles_Ex3) +
  coord_cartesian(ylim = c(0, 2)) +
  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_scales_mles_Ex3) + 
  ylab("Estimated scale") + 
  geom_hline(yintercept=1, linetype="dashed", color = "red")

>>>>

bibliography: CTRMstats.bib
csl: elsevier-harvard.csl
output:
  html_document: default
  rticles::elsevier_article:
    number_sections: true
    fig_caption: yes

@@

mean_n200<-hill_plot_values %>% group_by(x) %>% summarize(mean=mean(y))
p1<-hill_plot_values %>% ggplot() + geom_line(aes(x=x,y=y,group=rep), alpha=0.1) +
  coord_cartesian(ylim = c(0.5, 1.5)) +
  geom_line(aes(x=x, y=mean),colour="black",data=mean_n200) + 
  ylab("Estimated tail") +
  geom_hline(yintercept=0.8, linetype="dashed", color = "red")+
  xlab("Order Statistics")+
  ylab("Hill-Estimator of Tail Index")

@@

p2<-hill_plot_values %>% ggplot() + geom_line(aes(x=x,y=y,group=rep), alpha=0.1) +
  coord_cartesian(ylim = c(0.5, 1.5)) +
  geom_line(aes(x=x, y=mean),colour="black",data=mean_n1000) + 
  ylab("Estimated tail") +
  geom_hline(yintercept=0.8, linetype="dashed", color = "red")+
  xlab("Order Statistics")+
  ylab("Hill-Estimator of Tail Index")

@@

#logMoment estimator
logMom_Ex1_tail <-
  ggplot() + geom_line(aes(x = k, y = value, group = rep),
                       alpha = 0.05,
                       data = tbl_estimates_tail08_logMoms_Ex1) +
  coord_cartesian(ylim = c(0.5, 1.5)) +
  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_logMoms_Ex1) + 
  ylab("Estimated tail") + geom_hline(yintercept=0.8, linetype="dashed", color = "red")

#ml estimator
mle_Ex1_tail <-
  ggplot() + geom_line(aes(x = k, y = value, group = rep),
                       alpha = 0.05,
                       data = tbl_estimates_tail08_mles_Ex1) +
  coord_cartesian(ylim = c(0.5, 1.5)) +
  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_mles_Ex1) + 
  ylab("Estimated tail") + 
  geom_hline(yintercept=0.8, linetype="dashed", color = "red")

#Hill estimator
# hill_Ex1_tail <-
#   ggplot() + geom_line(data = tbl_estimates_tail08_hill_Ex1,
#                        aes(x = k, y = value, group = rep),
#                        alpha = 0.05) +
#   coord_cartesian(ylim = c(0.5, 1.5)) +
#   geom_line(data=means.tbl_hill_Ex1,aes(x=k, y=mw),colour="black") + 
#   ylab("Estimated tail") +
#   geom_hline(yintercept=0.8, linetype="dashed", color = "red")+ xlab("r")

@@

#logMoment estimator
logMom_Ex2_tail <-
  ggplot() + geom_line(aes(x = k, y = value, group = rep),
                       alpha = 0.05,
                       data = tbl_estimates_Ex2_Pareto_tail08_logMoms) +
  coord_cartesian(ylim = c(0.5, 1.5)) +
  geom_line(aes(x = k, y = mw), colour = "black", data = means.tbl_logMoms_Ex2) + 
  ylab("Estimated tail") + 
  geom_hline(yintercept=0.8, linetype="dashed", color = "red")

#ml estimator
mle_Ex2_tail <-
  ggplot() + geom_line(aes(x = k, y = value, group = rep),
                       alpha = 0.05,
                       data = tbl_estimates_Ex2_Pareto_tail08_mles) +
  coord_cartesian(ylim = c(0.5, 1.5)) +
  geom_line(aes(x = k, y = mw), colour = "black", data = means.tbl_mles_Ex2) + 
  ylab("Estimated tail") + 
  geom_hline(yintercept=0.8, linetype="dashed", color = "red")

# #Hill estimator
# hill_Ex2_tail <-
#   ggplot() + geom_line(aes(x = k, y = value, group = rep),
#                        alpha = 0.05,
#                        data = tbl_estimates_Ex2_Pareto_tail08_hill_times) +
#   coord_cartesian(ylim = c(0.5, 1.5)) +
#   geom_line(aes(x = k, y = mw), colour = "black", data = means.tbl_hill_times_Ex2) + 
#   ylab("Estimated tail") +
#   geom_hline(yintercept=0.8, linetype="dashed", color = "red")+ xlab("r")

@@

#logMoment estimator
logMom_Ex3_tail <-
  ggplot() + geom_line(aes(x = k, y = value, group = rep),
                       alpha = 0.05,
                       data = tbl_estimates_Example3_Exp_logMoms) +
  coord_cartesian(ylim = c(0.5, 1.5)) +
  geom_line(aes(x = k, y = mw), colour = "black", data = means.tbl_logMoms_Ex3) + 
  ylab("Estimated tail") + 
  geom_hline(yintercept=1, linetype="dashed", color = "red")

#ml estimator
mle_Ex3_tail <-
  ggplot() + geom_line(aes(x = k, y = value, group = rep),
                       alpha = 0.05,
                       data = tbl_estimates_Example3_Exp_mles) +
  coord_cartesian(ylim = c(0.5, 1.5)) +
  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_mles_Ex3) + 
  ylab("Estimated tail") + 
  geom_hline(yintercept=1, linetype="dashed", color = "red")

# #Hill estimator
# hill_Ex3_tail <-
#   ggplot() + geom_line(aes(x = k, y = value, group = rep),
#                        alpha = 0.05,
#                        data = tbl_estimates_Example3_Exp_hill_times) +
#   coord_cartesian(ylim = c(0.5, 10)) +
#   geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_hill_times_Ex3) + 
#   ylab("Estimated tail") + 
#   geom_hline(yintercept=1, linetype="dashed", color = "red")+ xlab("r")
# 
grid.arrange(
  arrangeGrob(logMom_Ex1_tail,logMom_Ex2_tail,logMom_Ex3_tail,top="log-Moment"),
  arrangeGrob(mle_Ex1_tail, mle_Ex2_tail, mle_Ex3_tail,top="MLE"),
  # arrangeGrob(hill_Ex1_tail,hill_Ex2_tail,hill_Ex3_tail,top="Hill"),
  ncol=2, top="Stability plots: tail parameter"
)
```

@@

#Example One
logMom_Ex1_scale <-
  ggplot() + geom_line(aes(x = k, y = value, group = rep),
                       alpha = 0.05,
                       data = tbl_scales_logMoms_Ex1) +
  coord_cartesian(ylim = c(0, 2)) +
  geom_line(aes(x = k, y = mw), colour = "black", means.tbl_scales_logMoms_Ex1) + 
  ylab("Estimated scale") +
  geom_hline(yintercept=1, linetype="dashed", color = "red")

mle_Ex1_scale <-
  ggplot() + geom_line(aes(x = k, y = value, group = rep),
                       alpha = 0.05,
                       data = tbl_scales_mles_Ex1) +
  coord_cartesian(ylim = c(0, 2)) +
  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_scales_mles_Ex1) + 
  ylab("Estimated scale") +
  geom_hline(yintercept=1, linetype="dashed", color = "red")

@@

logMom_Ex2_scale <-
  ggplot() + geom_line(aes(x = k, y = value, group = rep),
                       alpha = 0.05,
                       data = tbl_scales_logMoms_Ex2) +
  coord_cartesian(ylim = c(0, 2)) +
  geom_line(aes(x=k, y=mw),colour="black",means.tbl_scales_logMoms_Ex2) + 
  ylab("Estimated scale") + 
  geom_hline(yintercept=1, linetype="dashed", color = "red")

mle_Ex2_scale <-
  ggplot() + geom_line(aes(x = k, y = value, group = rep),
                       alpha = 0.05,
                       data = tbl_scales_mles_Ex2) +
  coord_cartesian(ylim = c(0, 2)) +
  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_scales_mles_Ex2) + 
  ylab("Estimated scale") + 
  geom_hline(yintercept=1, linetype="dashed", color = "red")

@@

logMom_Ex3_scale <-
  ggplot() + geom_line(aes(x = k, y = value, group = rep),
                       alpha = 0.05,
                       data = tbl_scales_logMoms_Ex3) +
  coord_cartesian(ylim = c(0, 2)) +
  geom_line(aes(x=k, y=mw),colour="black",means.tbl_scales_logMoms_Ex3) + 
  ylab("Estimated scale") + 
  geom_hline(yintercept=1, linetype="dashed", color = "red")

mle_Ex3_scale <-
  ggplot() + geom_line(aes(x = k, y = value, group = rep),
                       alpha = 0.05,
                       data = tbl_scales_mles_Ex3) +
  coord_cartesian(ylim = c(0, 2)) +
  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_scales_mles_Ex3) + 
  ylab("Estimated scale") + 
  geom_hline(yintercept=1, linetype="dashed", color = "red")
